Software Citation Principles

### 2016-03-21 sc-principles/software-citation-principles.tex
Updates from ShareLaTeX

Researcher            & benchmark software                       & \textbullet &             & \textbullet & \textbullet & \textbullet & \textbullet &             &            & \textbullet \\

@@

Indexer                     & build catalog of software               & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet &            & \textbullet \\
Domain group           & build catalog of software                & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet &             &            & \textbullet \\
Library\slash archive  & build catalog of software                & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet &             &            & \textbullet \\

@@

The software citation principles do not define what software should be cited, but rather, how software should be cited.
What software should be cited is the decision of the author(s) of the research work, in the context of community norms and practices, and in most scientific communities, these are currently in flux.
In general, we believe that any software on which a research product directly depends should be cited, if it significantly contributes to the research product.
Again, the specific decision of what is significant must be made by the author(s) of the product.
However, an illustrative example is the use of Microsoft Excel in research.
We suggest that if Excel is used to simply store and plot data, it does not need to be cited, but if it is used for statistical analysis, it should be.  Similarly, general software for conducting library research (e.g., JSTOR Mobile App), writing research papers (e.g., \LaTeX), scientific presentations (e.g., Powerpoint) or communications (e.g., Skype) should not be cited.''
This recommendation matches that of the Purdue Online Writing Lab: ``Do not cite standard office software (e.g. Word, Excel) or programming languages.  Provide references only for specialized software.''~\cite{powl-citing-software}

@@

\textbf{Unique identifiers}

The ``unique'' in a UID means that it points to a unique, specific software. However, multiple UIDs might point to the same software.  This is not recommended, but is possible.  We strongly recommend that if there is already a UID for a version of software, no additional UID should be
created.  Multiple UIDs can lead to split credit, which does not help anyone.  In particular, we
urge the use of standard DOIs as the UIDs for software. \katznote{This topic is discussed in detail in the `Unique Identification' section of \cite{10.7717/peerj-cs.1}}

%\LJHnote{not sure that multiple UIDs would be a recommended best practice as  this could cause conflicts} \katznote{LJH: not recommended, but likely will happen anyhow} \katznote{maybe discuss how identifiers are created}

>>>>

Researcher            & benchmark software                       & \textbullet &             & \textbullet & \textbullet & \textbullet & \textbullet &             & \textbullet & \textbullet \\

@@

Indexer                     & build catalog of software                & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet \\
Domain group           & build catalog of software                & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet &             & \textbullet & \textbullet \\
Library\slash archive & build catalog of software                & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet &             & \textbullet & \textbullet \\

@@

In the principles, we did not define what software should be cited, but how it should be cited.
What software should be cited is the decision of the author(s) of the research work, in the context of community norms and practices, and in most scientific communities, these are currently in flux.
In general, we believe that any software on which a research product directly depends should be cited, if it significantly contributes to the research product.
Again, the specific decision of what is significant must be made by the author(s) of the product.
However, an illustrative example is the use of Microsoft Excel in research.
We suggest that if Excel is used to simply store and plot data, it does not need to be cited, but if it is used for statistical analysis, it should be.  Similarly, general software for conducting library research (e.g., JSTOR Mobile App), writing research papers (e.g., \LaTeX), scientific presentations (e.g., Powerpoint) or communications (e.g., Skype) should not be cited.''
This recommendation matches that of the Purdue Online Writing Lab: ``Do not cite standard office software (e.g. Word, Excel) or programming languages.  Provide references only for specialized software.''~\cite{powl-citing-software}

@@

\textbf{Unique identifiers} \katznote{Is this discussion topic needed?  I would like to delete it.}

A UID points to a specific software, but multiple UIDs might point to the same software.
\LJHnote{not sure that multiple UIDs would be a recommended best practice as  this could cause conflicts} \katznote{LJH: not recommended, but likely will happen anyhow} \katznote{maybe discuss how identifiers are created}
